Universal Anonymous Signatures

### 2022-05-02 prism-backend/research/gsac/app-gsac.tex
Proving traceability of GSAC. Need to formalize SBCM and Encryption first...
Proofs for GSAC done (except correctnes...)

        \procedure{$\OBTISS(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\gpk,\isk,\Attrs) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
          \pcreturn \top \\
        }

        \procedure{$\OBTAIN(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs),\adv \rangle \\
          \CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
          \pcreturn \top \\
        }

@@

        \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \Issue(\gpk,\isk,\Attrs) \rangle \\
          \trans[\cid] \gets \utrans \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
          \pcreturn \top \\          
        }

@@

>>>>

        \procedure{$\OBTISS(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\gpk,\isk,\Attrs) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets (\uid,\cred,\Attrs) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTAIN(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid,\cred,\Attrs) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \Issue(\gpk,\isk,\Attrs) \rangle \\
          \trans[\cid] \gets \utrans;~
          \CRED[\cid] \gets (\uid,\cdot,\Attrs) \\
          \pcreturn \top \\          
        }

@@

\commentwho{Jesus}{Strictly, in our generic construction we require IND-CCA (is
  that a strict requirement? or can it be downgraded to IND-CPA?), but in the
  following concrete instantiation, we use ElGamal, which is IND-CPA. However,
  we actually ``lift'' ElGamal with NIZKs of the encrypted plaintexts, which is
  essentially IND-CCA as far as I know. Still, make sure to mention that.}

\begin{proof}[\thmref{thm:correctness-gsac}]
  \todo{XXX}
\end{proof}

\begin{proof}[\thmref{thm:anonymity-gsac}]
  We prove that the probability of an adversary distinguishing signatures by
  challenge users is negligible. For the proof, we restrict to the case of
  allowing only one query to the challenge oracle. The extension to a polynomial
  number of queries given in \cite{bsz05} applies here, with the corresponding
  security loss.

  We begin with game $G_0=\ExpGSACAnonb$. From it, we build $G_1$, where we
  simply replace the \NIZKSetup functions for $\NIZKRel_{\Sign}$ and
  $\NIZKRel_{\Open}$ within the \Setup algorithm. $G_1$ is indistinguishable
  from $G_0$ due to the zero-knowledge property of the NIZK systems.

  From $G_1$, we build $G_2$, where within the challenge signature produced by
  \CHALb, we replace the \Ccom value encrypted within \Sign with a random
  string of the appropriate length (e.g., the same length of the encrypted
  message in $G_1$). The corresponding proof for $\NIZKRel_{\Sign}$ is thus
  also simulated. The zero-knowledge and simulation-extractability properties
  of the NIZKs for $\NIZKRel_{\Sign}$, and IND-CCA of the encryption
  scheme, ensure that the result is indistinguishable to the adversary.

  Now, observe that in $G_2$, the challenge signature received by the adversary
  is completely independent from the challenge bit $b$. Moreover, as argued,
  $G_2$ is indistinguishable from $G_0$, where the adversary plays the original
  \ExpGSACAnonb game. Thus, our generic construction of \GSAC satisfies
  anonymity, except with negligible probability.
  %
  \qed
\end{proof}

\begin{proof}[\thmref{thm:trace-gsac}]
  Assuming the NIZK systems are sound, we build an adversary against existential
  unforgeability of the signature scheme for blocks of committed messages.
  %
  Consider the following events:

  \begin{description}
  \item[$O$.] The \Open algorithm returns $\bot$.
  \item[$J$.] The \Judge algorithm returns $0$.
  \item[$D$.] No credential owned by a user in \CU contains \DAttrs.
  \end{description}

  Given these events, the adversary wins if:

  \begin{description}
  \item[$W_1 = O$.] \Open returns $\bot$ (line 5 of \ExpGSACTrace).
  \item[$W_2 = \overline{O} \land J$.] \Open does not fail, but \Judge rejects
    the output of \Open (line 7 of \ExpGSACTrace).
  \item[$W_3 = \overline{O} \land \overline{J} \land D$.] \Open does not fail,
    \Judge accepts the output by \Open, but no corrupt user has a credential
    containing \DAttrs (line 8 of \ExpGSACTrace).
  \end{description}

  Clearly, since the group signature is verified at step 4 of the game, if
  verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
  \Ec,\DAttrs) \in \NIZKLang_{\Sign}$, except with negligible probability
  $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
  adversary described above are disjoint. Thus:

  \begin{equation}
    \AdvGSACTrace(\secpar) = \Pr[W_1]+\Pr[W_2]+\Pr[W_3]+\negl(\NIZKsecpar)
  \end{equation}

  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\DAttrs)
  \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
  we know that \Open does not abort due to rejection of the signature by
  \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
  $\Ec = \EEnc(\opk,\Ccom)$ which, by correctness of the encryption algorithm,
  implies that $\Ccom = \EDec(\osk,\Ec)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
  Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
  compute the opening proof \oproof, and return $(\upk,\oproof)$.

  $\Pr[W_2] = 0$ is similarly deduced from soundness of $\NIZK_{\Sign}$ and
  completeness of $\NIZK_{\Open}$, since the opening proof is computed
  honestly in line 6 of \ExpGSACTrace.

  Finally, assume that there is an adversary $\adv$ against \ExpGSACTrace that
  wins by event $W_3$. Then, it is straight forward to build an adversary \advB
  against unforgeability of the signature scheme on blocks of committed
  messages. Namely, \advB creates the parameters with \Setup and the opening
  key pair with \OKeyGen, but instead of running \IKeyGen, sets the verification
  key to the one received in the \ExpSBCMOMF game. In calls by $\adv$ to \OBTISS
  and \ISSUE oracles, \advB replaces the \Issue algorithm with corresponding
  calls to its $\langle \cdot,\SBCMSign \rangle$ oracle. The other oracles are
  unchanged. Without loss of generality, suppose that $\adv$ makes a total of
  $n$ queries to \OBTISS and \ISSUE, combined; which implies that \advB makes
  a total of $n$ queries to its own oracle. If, in such an execution, $\adv$
  wins by event $W_3$, it means that it has produced a signature \sig, revealing
  attribute set \DAttrs, that is accepted by \Verify, for which \Open does not
  fail, and for which an honestly generated open proof is accepted by \Judge,
  but such that no issued credential contains \DAttrs. Soundness of
  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\Attrs \cup
  \lbrace \usk \rbrace$, and $\DAttrs \subseteq \Attrs$; but \sig has not been
  produced via a call to the $\langle \cdot,\SBCMSign \rangle$ oracle. Thus,
  \advB can output at least $n+1$ valid signatures, which contradicts security
  of \SBCM.
  %
  By assumption of security of \SBCM, $\Pr[W_3]$ must therefore be negligible in
  $\SBCMsecpar$ and, consequently: $\AdvGSACTrace(\secpar) = \negl(\SBCMsecpar)+
  \negl(\NIZKsecpar)$, which is negligible.  
  \qed
\end{proof}

\begin{proof}[\thmref{thm:frame-gsac}]
  We build an adversary \advB who, given an adversary $\adv$ against
  \ExpGSACNonframe, breaks the hiding property of \C.

  To do so, we start with $G_0=\ExpGSACNonframe$. From $G_0$, we build $G_1$
  by replacing $\NIZKSetup^{\NIZKRel_{\Issue}}$ and  $\NIZKSetup^{\NIZKRel_{\Sign}}$
  with $\NIZKSimSetup^{\NIZKRel_{\Issue}}$ and $\NIZKSimSetup^{\NIZKRel_{\Sign}}$,
  within the \Setup algorithm. Due to the zero-knowledge property of both
  $\NIZK^{\NIZKRel_{\Issue}}$ and $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
  indistinguishable from $G_0$.

  We now build \advB from $G_1$. Recall that \advB is an adversary against
  hiding of \C and, thus, receives a commitment \Ccom, committing to one out
  of two possible messages, $\msg_0$ and $\msg_1$, which \advB picks at random
  from $\AttrSpace$. \advB initializes everything as $G_1$ and, in addition,
  chooses a random integer $u \in [q]$, where $q$ will be the maximim number of
  users to let $\adv$ create via calls to the \HUGEN oracle (note though that
  $q$ can be as large as desired, as it remains a polynomial function of the
  security parameter). In the $u$-th call to the \HUGEN oracle, \advB ignores
  sets $(\upk,\usk)$ to $(\Ccom,\bot)$. Calls to the \OBTAIN and \SIGN oracles
  are dealt with as usual, except when $\adv$ requests credentials or signatures
  on behalf of the $u$-th user. In that cases, \advB simulates the corresponding
  NIZK proofs by calling $\NIZKSim^{\NIZKRel_{\Issue}}$ or
  $\NIZKSim^{\NIZKRel_{\Sign}}$, respectively. Due to the
  simulation-extractability property of both NIZK systems, the output produced
  by the oracles is indistinguishable from that in $G_1$ and, consequently, from
  $G_0=\ExpGSACNonframe$.

  Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\DAttrs,
  \msg,\upk,\pi)$, where $(\sig,\DAttrs,\msg)$ are accepted by \Verify, and
  $(\upk,\pi,\sig,\DAttrs,\msg)$ are accepted by \Judge. Thus, after soundness
  of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that
  \upk is the correct public key associated to an honest user \uid, but as per
  the winning condition, \sig has not been produced via a call to the \SIGN
  oracle for a \cid owned by \uid. Therefore, we can extract the \usk
  corresponding to \upk from the $\pi_{\sig}$ proof. Since executions in the
  environment prepared by \advB are indistinguishable to $\adv$ from executions
  of $G_0$, we can assume that the probability that the \uid associated to the
  \sig output by $\adv$ equals $1/q$. In that case, \usk precisely matches
  $\msg_b$, and \advB wins the hiding game against \C. Since we assume \C
  to be hiding, this probability must therefore be negligible.   
  \qed
\end{proof}

### 2022-05-02 prism-backend/research/gsac/security-gsac.tex
Proofs for GSAC done (except correctnes...)

@@

\begin{proof}[\thmref{thm:correctness-gsac}]
  \todo{XXX}
\end{proof}

\begin{theorem}[Anonymity of \GSACGen]
  \label{thm:anonymity-gsac}
  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge and
  simulation-extractable, our \GSACGen construction satisfies anonymity as
  defined in \defref{def:anonymity-gsac}.
\end{theorem}

\begin{proof}[\thmref{thm:anonymity-gsac}]
  %
  \qed
\end{proof}

\begin{theorem}[Traceability of \GSACGen]
  \label{thm:trace-gsac}
  If the underlying scheme for \todo{xxx}, then our \GSACGen construction
  satisfies traceability as defined in \defref{def:trace-gsac}, except
  with negligible probability.
\end{theorem}

\todo{\usk belongs to \AttrSpace! I think this can lead to malleability attacks.
  Make them disjoint?}

\begin{proof}[\thmref{thm:trace-gsac}]
  \qed
\end{proof}

\begin{theorem}[Non-frameability of \GSACGen]
  \label{thm:frame-gsac}
  If the underlying schemes for \todo{xxx}, then our \GSACGen construction
  satisfies non-frameability as defined in \defref{def:frame-gsac}, except with
  negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:frame-gsac}]
  \qed
\end{proof}

>>>>

For the sake of brevity, here we just enuntiate the main theorems related to
correctness and security of \GSAC, and defer the full proofs to
\appref{sapp:gsac-proofs}.

@@

\begin{theorem}[Anonymity of \GSACGen]
  \label{thm:anonymity-gsac}
  If the underlying $\NIZK^{\NIZKRel_{\Sign}}$ scheme is zero-knowledge and
  simulation-extractable, and the encryption system is IND-CCA secure,
  our \GSACGen construction satisfies anonymity as defined in
  \defref{def:anonymity-gsac}.
\end{theorem}

\begin{theorem}[Traceability of \GSACGen]
  \label{thm:trace-gsac}
  If the underlying $\NIZK^{\NIZKRel_{\Sign}}$ scheme is sound, the
  $\NIZK^{\NIZKRel_{\Open}}$ is  complete, the public-key encryption algorithm
  is correct, and the signature scheme for blocks of committed messages is
  one-more unforgeable, then our \GSACGen construction satisfies traceability as
  defined in \defref{def:trace-gsac}, except with negligible
  probability.
\end{theorem}

\begin{theorem}[Non-frameability of \GSACGen]
  \label{thm:frame-gsac}
  If the underlying scheme for $\NIZK^{\NIZKRel_{\Issue}}$,
  $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$ are sound,
  zero-knowledge, and simulation-extractable, and
  the commitment scheme \C is hiding, then our generic \GSACGen construction
  satisfies non-frameability as defined in \defref{def:frame-gsac}, except with
  negligible probability.
\end{theorem}
